disturbance chronologies

### 2017-06-01 analysis/analysis_disturbance_chronos.Rmd
update chronos

```{r}
source(paste0(di, 'script/R/rw_byTree.R'))
source(paste0(di, 'script/R/bai_piovesan.R'))

@@

>>>>

```{r}
source(paste0(di, 'script/R/rw_byTree.R'))
source(paste0(di, 'script/R/bai_piovesan.R'))
source(paste0(di, 'script/R/computeGC.R'))

@@

```{r}

gc_caL <- computeGC(caL_tree, ws=10, prefijo = 'CA')
gc_caH <- computeGC(caH_tree, ws=10, prefijo = 'CA')
gc_sj <- computeGC(sj_tree, ws=10, prefijo = 'SJ')

	GCper=100*((mean(m2[,1])-mean(m1[,1]))/mean(m1[,1]))  ##PGC

	GCperneg=100*((mean(m1[,1])-mean(m2[,1]))/mean(m2[,1])) ###NGC
	GCfin=rbind(GCfin, c(i, j, GCper, GCperneg))
	names(GCfin)=c("tree2", "year", "GCper", "GCperneg")

	GCper = 100

GCfin2$GCfinal <- ifelse(GCfin2$GCper>0, GCfin2$GCper, -1*GCfin2$GCperneg) ###pongo para los positivos el PGC, para los negativos el NGC

GCfin2<<-GCfin2

xx <- getGC(caL_tree, ws=10, prefijo='CA')

GCfin2 <- data.frame(GCper = GCper, GCperneg = GCperneg)

AGC2=function(RWL){

  GC=as.data.frame(NULL)

  #
  for (n in 1:ncol(RWL)){
    series <- as.data.frame(RWL[, n])
    series$year=as.numeric(row.names(RWL))
    series=subset(series, !is.na(series[1]))
    tree=as.numeric(substr(colnames(RWL)[n],3,4))
    tree2=as.numeric(substr(colnames(RWL)[n], 5,5))
    if(!is.na(tree2)){
      tree3=as.numeric(substr(colnames(RWL[n]),3,5))}
    else {tree3=tree}
    series$tree=as.numeric(tree3)

    GC=rbind(GC, series)
    }
  names(GC)[1]="RW"
  GC2=aggregate(GC[,1], by=list(year=GC$year,tree=GC$tree), mean)
  names(GC2)[3]="RW"
  GC2=GC2[order(GC2$tree, GC2$year),]

  GC2$tree2=1
  for (i in 2:nrow(GC2)){
    if(GC2$year[i]<GC2$year[i-1]) GC2$tree2[i]=1+GC2$tree2[i-1] else GC2$tree2[i]=GC2$tree2[i-1]}
  GC2<<-GC2
  }

AGC3=function(RWL, n)
{
GCfin2=data.frame(NULL)

for (i in 1:max(RWL[,4])) {

  series=subset(RWL, tree2==i)

  GCfin=data.frame(NULL)

  for (j in (min(series$year)+n):(max(series$year)-n)){

    M2=subset(series, series$year>=j & series$year<(j+n-1))
    M1=subset(series, series$year<(j-1) & series$year>=(j-n))

	GCper=100*((mean(M2[,3])-mean(M1[,3]))/mean(M1[,3]))  ##PGC
	GCperneg=100*((mean(M1[,3])-mean(M2[,3]))/mean(M2[,3])) ###NGC

	GCfin=rbind(GCfin, c(i, j, GCper, GCperneg))
	names(GCfin)=c("tree2", "year", "GCper", "GCperneg")
}
GCfin2=rbind(GCfin2, GCfin)
}
GCfin2$GCfinal=
  ifelse(GCfin2$GCper>0, GCfin2$GCper, -1*GCfin2$GCperneg) ###pongo para los positivos el PGC, para los negativos el NGC
GCfin2<<-GCfin2
}

rr <- AGC2(sj)
rr2 <- AGC3(rr, 10)

RWL <- rr
n <- 10
1:max(RWL[,4])
i <- 1 
series=subset(RWL, tree2==i)

rangej <- (min(series$year)+n):(max(series$year)-n)
j <- rangej[1]

M2=subset(series, series$year>=j & series$year<(j+n-1))
M2b =subset(series, series$year<(j+n-1))

rr

head(rr)

range <- (min(rr$year) + 10):(max(rr$year) - 10)

series <- subset(rr, tree2 == 1)
M2 = subset(series, series$year>=j & series$year<(j+n-1))

j<- 1931
n <- 10
